% Structured according to Gertiser's feedback:
% 1) Worum geht es?
% 2) Ziel und Anforderungen
% 3) Umsetzung -> Grobkonzept
% 4) Resultate
% 5) Aufbau der Arbeit

The objective  of our next project  (\emph{Project 4}) will be  to construct a
device  capable  of  monitoring  photovoltaic  modules  used  in  solar  power
arrays. In order to  be able to test that device  in a laboratory environment,
the  aim of  this project  is to  construct a  device capable  of emulating  a
photovoltaic module.

The primary characteristics  of our device should be compactness  (usable in a
standard  laboratory environment),  the  capability to  emulate varying  solar
irradiation levels,  being able  to be  used in  series with  other emulators,
effiency with  regards to  power consumption  and losses,  and to  emulate the
voltage-current  line  of  an  actual  PV  module. A  more  detailed  list  of
the  required specifications  can  be  found in  appendix  \code{XXX (link  to
Lastenheft)}. %TODO

At  the core  of  our device  lie a  microcontroller  and a  constant-current,
constant-voltage step-down converter.  The  microcontroller is responsible for
programming and  controlling the  device, whereas  the step-down  converter is
used  to  generate the  output  voltage  and  output  current of  the  desired
operating point  from a DC power  supply. The entire design is  based around a
custom  PCB. This enables  us to  get very  close in  behavior to  a porential
mass-produced  product since  trace lenghts,  routing and  component placement
are  crucial  (see  also  section \ref{sec:verification},  beginning  on  page
\pageref{sec:verification}).

Aside from a professionally printed PCB,  the device has a simple yet powerful
user interface  which can be  controlled by a  push-twist button and  a modern
OLED display. In addition to direct  physical interaction, the device can also
be remotely monitored and controlled from a  PC via USB interface and a custom
software. Said  software is  built  on  the Qt  application  framework and  is
compatible with all major operating systems~\cite{ref:qt}. With regards to its
capability  to  emulate  PV  arrays,  our device  can  emulate  quite  complex
configurations of  cells thanks to  an efficient use of  computation resources
and its powerful microprocessor.

Sections  \ref{sec:task}   (p.  \pageref{sec:task}ff)   and  \ref{sec:concept}
(p.   \pageref{sec:concept}ff)   of   this   report   deal   with   the   task
itself  and  the  basic   concept  behind  our  solution. Component  selection
and   PCB  design   are  documented   in  sections   \ref{sec:components}  (p.
\pageref{sec:components}ff)   and   \ref{sec:pcb}   (p.   \pageref{sec:pcb}ff)
respectively, while section \ref{sec:software}  is concerned with the software
(p.  \pageref{sec:software}ff).   Lastly, section  \ref{sec:verification}  (p.
\pageref{sec:verification}ff) deals  with testing  the device  including error
analysis, and the  conclusion can be found in  section \ref{sec:conclusion} on
page \pageref{sec:conclusion}.
